### 2021-04-20 README.rmd
minor corrections after first CRAN human check

To contribute to `geocmeans`, please follow these [guidelines](CONTRIBUTING.md).

Please note that the `geocmeans` project is released with a [Contributor Code of Conduct](CONDUCT.md). By contributing to this project, you agree to abide by its terms.

@@

`geocmeans` version 0.1.0 is licensed under [GPL2 License](LICENSE.txt).

>>>>

To contribute to `geocmeans`, please follow these [guidelines](https://github.com/JeremyGelb/geocmeans/blob/master/CONTRIBUTING.md).

Please note that the `geocmeans` project is released with a [Contributor Code of Conduct](https://github.com/JeremyGelb/geocmeans/blob/master/CONDUCT.md). By contributing to this project, you agree to abide by its terms.

@@

`geocmeans` version 0.1.0 is licensed under [GPL2 License](https://github.com/JeremyGelb/geocmeans/blob/master/LICENSE.txt).
